---
title: "Analysis of Litecoin as a Store of Value"
author: "Samuel Johnson"
date: '2022-08-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(lubridate)
#Reading in the files that we are going to use for the analysis
ltc <- read.csv("/home/sam/R/LitecoinAn/LTC-USD.csv")

#Formatting the dates
ltc$Date <- as.Date(ltc$Date)

#Removing duplicates
ltc %>% 
  distinct(.keep_all = TRUE)

#Confirming that our data has been sufficiently cleaned
glimpse(ltc)
str(ltc)
colnames(ltc)
```
## Litecoin Analysis

This Analysis will cover why Litecoin is a successful cryptocurrency and educate you on its potential. This is not financial advice. Please do your own research.  
The research question

+ Does Litecoin function as a Store of Value?

Litecoin is a cryptocurrency running on a Proof of Work blockchain. Proof of Work refers to a process where miners(those participating) must use computers to guess a nonce in order to unlock a block and earn the mining reward. Litecoin has a set cap of 84 million and a halving cycle every four years, much like Bitcoin. This means that scarcity is created since the amount of Litecoin is halved during this interval. For example, in 2013, the initial reward per block was 50 LTC. Four years later, in 2017, this was halved to 25. 
Unlike Bitcoin though, Litecoin creates blocks every 2.5 minutes instead of Bitcoin's 10. This lighter algorithm and faster block time is designed to make Litecoin an ideal currency for quick and hard transactions. Additionally, Litecoin acts like a test network for Bitcoin, having implemented the Mimble Wimble privacy protocol before Bitcoin as well as the Lightning Network among other projects.  
Furthermore, wherever Bitcoin is sold, Litecoin is also. According to the Litecoin Whitepaper, it represents Digital Silver if Bitcoin is Digital Gold.

The data represented here is from 2014-2022 and was pulled from [Yahoo Finance](https://finance.yahoo.com/quote/LTC-USD/history?period1=1410825600&period2=1661731200&interval=1d&filter=history&frequency=1d&includeAdjustedClose=true).

Since Litecoin is designed to be the Silver to Bitcoin's Gold. We will be looking at whether Litecoin functions well as a store of value. According to [investopedia](https://www.investopedia.com/terms/s/storeofvalue.asp), stores of value need to fulfill the following criteria. 

*A store of value is an asset that maintains its value, rather than depreciating. 
*Gold and other precious metals are good stores of value because their shelf lives are essentially perpetual.
*A nation's currency must be a reasonable store of value for its economy to function smoothly.

To determine how well Litecoin functions as a store of value, we will measure its Daily closing price, to reflect the maintenance of value, and trading volume, to reflect its value as a currency. As long as miners contribute to the network, the Litecoin blockchain will serve perpetually.

## Daily closing price

The Daily closing price has been displayed to give an idea of how volatile Litecoin can be in addition to how profitable it can be. 
Litecoin tends to correlate heavily with Bitcoin per this chart, spiking in price when BTC does. This spike correlates to the BTC halving. 
Litecoin also has its own halving cycle detached from BTC which we can observe in this chart as well. In between the spikes correlating with BTC we have smaller runs that peak up in 2019 and 2015. This correlated to  LTC halving at that time. 

Below is the code used for calculating the daily closing price, accompanied by a line chart. 
```{r}
#Plotting out and printing the daily closing price
closing_price <- ggplot(data = ltc) + geom_line(mapping = aes(x = Date, y = Close)) +
  labs(title = "Closing price of LTC", subtitle = "From April 2013 - August 2022", caption = "This is not financial advice.")

closing_price
```

## Daily Volume 

Just like its historical counterpart, Silver, Litecoin appears to be quite successful as a currency. As can be seen from the graph below, holding is encouraged by Litecoin because its closing price correlates to its trading volume which is high and consistent.

Below is the daily volume of Litecoin transactions. 
```{r}
volume <- ggplot(data = ltc) + geom_line(mapping = aes(x = Date, y = Volume)) +
  labs(title = "Volume of LTC", subtitle = "From April 2013 - August 2022", caption = "This is not financial advice.")

volume
```

And here is the code used to show the correlation between volume and closing price. 
```{r}
#Plotting Volume vs closing

volume_vs_closing <- ggplot(data = ltc) + geom_smooth(mapping = aes(y = Volume, x = Close)) +
  labs(title = "Volume vs Closing of LTC", subtitle = "From April 2013 - August 2022", caption = "This is not financial advice.")

volume_vs_closing
```

## Conclusions 

Litecoin consistently maintains its place among the top 50 cryptocurrencies on [coinmarketcap.com](www.coinmarketcap.com). The Proof of Work Blockchain creates a competitive incentive to maintain the network while creating scarcity. 
Litecoin's fundamentals can be reflected in its incredibly high trading volume. 
Furthermore, while Litecoin has proven volatile, it is steadily rising in price, thanks to its price correlation with Bitcoin and its halvings, in addition to the added scarcity from its own mining reward halvings. 

## References
+ CoinMarketCap(2022), www.coinmarketcap.com
+ Downey(2022), What is a Store of Value, https://www.investopedia.com/terms/s/storeofvalue.asp
+ Yahoo Finance(2022), https://finance.yahoo.com/quote/LTC-USD/history?period1=1410825600&period2=1661731200&interval=1d&filter=history&frequency=1d&includeAdjustedClose=true


## The code used to produce this report

```{r eval = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(lubridate)
#Reading in the files that we are going to use for the analysis
ltc <- read.csv("/home/sam/R/LitecoinAn/LTC-USD.csv")

#Formatting the dates
ltc$Date <- as.Date(ltc$Date)

#Removing duplicates
ltc %>% 
  distinct(.keep_all = TRUE)

#Confirming that our data has been sufficiently cleaned
glimpse(ltc)
str(ltc)
colnames(ltc)

#Plotting out and printing the daily closing price
closing_price <- ggplot(data = ltc) + geom_line(mapping = aes(x = Date, y = Close)) +
  labs(title = "Closing price of LTC", subtitle = "From April 2013 - August 2022", caption = "This is not financial advice.")

closing_price

#Plotting the daily volume
volume <- ggplot(data = ltc) + geom_line(mapping = aes(x = Date, y = Volume)) +
  labs(title = "Volume of LTC", subtitle = "From April 2013 - August 2022", caption = "This is not financial advice.")

volume

#Plotting Volume vs closing

volume_vs_closing <- ggplot(data = ltc) + geom_smooth(mapping = aes(y = Volume, x = Close)) +
  labs(title = "Volume vs Closing of LTC", subtitle = "From April 2013 - August 2022", caption = "This is not financial advice.")

volume_vs_closing
```
